% !TeX program = lualatex
% !BIB program = bibtex
% Auriga theme
% https://github.com/anishathalye/auriga

\documentclass[14pt,aspectratio=169]{beamer}
\usepackage{pgfpages}
\usepackage{fancyvrb}
\usepackage{tikz}
\usepackage{pgfplots}

\usepackage[style=authortitle,backend=bibtex]{biblatex}
\addbibresource{../Paper/references.bib}
\addbibresource{../NonlinearBiquad/Paper/references.bib}
\addbibresource{references.bib}

% \ifnotes
% \setbeamertemplate{note page}[plain]
% \setbeameroption{show notes on second screen=right}
% \fi

\usetheme{auriga}
\usecolortheme{auriga}

\usepackage{hyperref}

% define some colors for a consistent theme across slides
\definecolor{red}{RGB}{181, 23, 0}
\definecolor{blue}{RGB}{0, 118, 186}
\definecolor{gray}{RGB}{146, 146, 146}

\title{Stable Structures for Nonlinear Biquad Filters}

\author{Jatin Chowdhury}

\institute[shortinst]{Center for Computer Research in Music and Acoustics (CCRMA)}

\def\DAFX{}

\begin{document}

{
  % rather than use the frame options [noframenumbering,plain], we make the
  % color match, so that the indicated page numbers match PDF page numbers
  \setbeamercolor{page number in head/foot}{fg=background canvas.bg}
  \begin{frame}
    \titlepage
  \end{frame}
}

\begin{frame}{Outline}
    \begin{itemize}
        \setlength\itemsep{0.8em}
        \item Review: Biquad Filters
        \item Nonlinear Biquad Filter
        \item Nonlinear Feedback Filter
        \item Stability analysis
        \item Analog modelling
    \end{itemize}
\end{frame}

\begin{frame}{Motivation}
    \begin{itemize}
        \item Can we develop interesting nonlinear audio effects, outside of virtual analog?
        \item Can we analyze these nonlinear effects, and learn to use them intelligently.
        \item Can we use these nonlinear effects for analog modelling?
    \end{itemize}
\end{frame}

\input{slides/nonlinear_filters}

\begin{frame}{Future Work}
    \begin{itemize}
        \setlength\itemsep{0.8em}
        \item How to choose nonlinear functions for a desired pole movement?
        \item How do the harmonics generated by the nonlinear functions affect the output signal?
        \item How can these filters be integrated into audio effects in a user-friendly way?
    \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
    \begin{itemize}
        \setlength\itemsep{0.8em}
        \item We have developed two structures for implementing nonlinear biquad filters.
        \item We have developed constraints for ensuring the stability of these filters.
        \item We have shown some possibilities for using nonlinear filters for analog modelling.
        \item We have developed open-source audio plugins demonstrating these structures.\footnote{\url{https://github.com/jatinchowdhury18/ComplexNonlinearities}}
    \end{itemize}
\end{frame}

\begin{frame}{}
    \begin{centering}
        \vskip5ex plus 1filll
        {\usebeamerfont{title page title}\usebeamercolor[fg]{title page} Thank you!\\[1.5ex]}
        \vskip0pt plus 1filll
    \end{centering}
\end{frame}

\end{document}
